Leadership across cultures and contexts: an exploratory analysis

### 2020-05-11 leadership_across_cultures_contexts.Rmd
Added ggsave's in main text

Within benefit/cost dimensions, there was relatively more evidence for mating and territory benefits than costs for both leaders and followers, and equal levels of evidence for protection from vs. risk of harm. For leaders compared to followers, there were noticably higher odds ratios for inclusive fitness benefits, material resources, and social services. See Figure \@ref(fig:benefitcostratio).

```{r benefitcostratio, fig.width=10, fig.cap="The odds ratios of finding evidence of a benefit vs. a cost in a text record for leaders and followers, by each dimension of benefits and costs. Odds ratios estimated using a mixed effects logistic regression model of evidence for (0/1) as a function of each dimension (e.g., Mating, Food), a term indicating if the evidence was for a benefit or cost, and their interaction, with random intercepts for author nested within culture. Separate models were fit for leaders and followers. X-axis is on a log scale."}
plot_bc_OR
```

@@

```{r heatmapdrop1, fig.width=12, fig.cap="Leadership dimensions and features that varied by group context, subsistence strategy, continental region, and/or leader sex. A. Leadership dimensions. B. Leadership features. Colors represent the relative change in AIC value after dropping that factor from a multiple logistic mixed effects regression model. Yellow: including factor improved fit relative to other factors. Black: including factor did not improve fit relative to other factors. Delta AIC values were standardized by rows, and therefore can only be compared within rows."}
heatmap_drop1 + guides(fill='none') + heatmap_features_drop1 + plot_annotation(tag_levels = 'A')
```

@@

highstatus_plot <- highstatus_plot + scale_x_log10()
highstatus_plot + plot_elastic_status + 
  plot_annotation(
    title = 'Predictors of High status',
    tag_levels = 'A', 
    caption = 'Odds ratio', 
    theme=theme(plot.caption=element_text(hjust=0.5, size=12, margin=margin(t=0)))
    )

@@

coercive_plot <- coercive_plot + scale_x_log10()
coercive_plot + plot_elastic_coercive +
  plot_annotation(
    title = 'Predictors of Coercive authority',
    tag_levels = 'A', 
    caption = 'Odds ratio', 
    theme=theme(plot.caption=element_text(hjust=0.5, size=12, margin=margin(t=0)))
    )

@@

```{r featuressupportplot, fig.width=10, fig.cap="Support of each feature variable at the levels of text records and cultures. Feature support at the text record was defined as the adjusted proportion of text records with evidence for at least one underlying variable in the feature. Feature support at the culture level was defined as the proportion of cultures with evidence for the feature in at least text record in the culture."}
plot_features_support
```

>>>>

Within benefit/cost dimensions, there was relatively more evidence for mating and territory benefits than costs for both leaders and followers, and equal levels of evidence for protection from harm vs. risk of harm. For leaders compared to followers, there were noticably higher odds ratios for inclusive fitness benefits, material resources, and social services. See Figure \@ref(fig:benefitcostratio).

```{r benefitcostratio, fig.width=10, fig.cap="The odds ratios of finding evidence of a benefit vs. a cost in a text record for leaders and followers, by each dimension of benefits and costs. Odds ratios estimated using a mixed effects logistic regression model of evidence for (0/1) as a function of each dimension (e.g., Mating, Food), a term indicating if the evidence was for a benefit or cost, and their interaction, with random intercepts for author nested within culture. Separate models were fit for leaders and followers. X-axis is on a log scale."}
ggsave(file='Figures/plot_bc_OR.pdf', plot_bc_OR, width = 9, height = 5)
plot_bc_OR
```

@@

```{r heatmapdrop1, fig.width=12, fig.cap="Leadership dimensions and features that varied by group context, subsistence strategy, continental region, and/or leader sex. A. Leadership dimensions. B. Leadership features. Colors represent the relative change in AIC value after dropping that factor from a multiple logistic mixed effects regression model. Yellow: including factor improved fit relative to other factors. Black: including factor did not improve fit relative to other factors. Delta AIC values were standardized by rows, and therefore can only be compared within rows."}

p <- heatmap_drop1 + guides(fill='none') + heatmap_features_drop1 + plot_annotation(tag_levels = 'A')
ggsave(filename = 'Figures/heatmap_drop1.pdf', p, width = 14, height = 5)

p
```

@@

highstatus_plot <- highstatus_plot + scale_x_log10()
p <- 
  highstatus_plot + plot_elastic_status + 
  plot_annotation(
    title = 'Predictors of High status',
    tag_levels = 'A', 
    caption = 'Odds ratio', 
    theme=theme(plot.caption=element_text(hjust=0.5, size=12, margin=margin(t=0)))
  )

ggsave('Figures/highstatus_plot.pdf', p, width=10, height = 7)

p
```

@@

coercive_plot <- coercive_plot + scale_x_log10()
p <-
  coercive_plot + plot_elastic_coercive +
  plot_annotation(
    title = 'Predictors of Coercive authority',
    tag_levels = 'A', 
    caption = 'Odds ratio', 
    theme=theme(plot.caption=element_text(hjust=0.5, size=12, margin=margin(t=0)))
    )
ggsave('Figures/coercive_plot.pdf', p, width = 8, height = 4)
p
```

@@

```{r featuressupportplot, fig.width=10, fig.cap="Support of each feature variable at the levels of text records and cultures. Feature support at the text record was defined as the adjusted proportion of text records with evidence for at least one underlying variable in the feature. Feature support at the culture level was defined as the proportion of cultures with evidence for the feature in at least text record in the culture."}

ggsave('Figures/plot_features_support.pdf', plot_features_support, width = 10, height = 5)
plot_features_support
```
